Function

### 2021-06-17 Function.Rmd

```{r}
vcf_files1 <- list.files(system.file("extdata", package="MutationalPatterns"), pattern = ".vcf", full.names = TRUE)
vcf_files <- vcf_files1[-c(1,2,3,7)]
sample_names <- c("colon1", "colon2", "colon3", "intestine1", "intestine2", "intestine3", "liver1", "liver2", "liver3")
vcfs <- read_vcfs_as_granges(vcf_files, sample_names, ref_genome)
tissue <- c(rep("colon",3), rep("intestine",3), rep("liver",3))
```

@@

@@

>>>>

```{r}
vcf_files1 <- list.files(system.file("extdata", package="MutationalPatterns"), pattern = ".vcf", full.names = TRUE)
#vcf_files <- vcf_files1[-c(1,2,3,7)]
vcf_files <-vcf_files1[c(4,5,6)]
sample_names <- c("colon1", "colon2", "colon3")
vcfs <- read_vcfs_as_granges(vcf_files, sample_names, ref_genome)
tissue <- c(rep("colon",3))
```

@@

```{r}
Bayes_function <- function(mutation, signature, sample, nmf_matrix, mutation_matrix){
  #Pr(Mutation|Signature)
  prob_mut_given_sig <- nmf_matrix$signatures[mutation,signature]/sum(nmf_matrix$signatures[,signature])
  #Pr(Signature)
  prob_sig <- nmf_matrix$contribution[signature,sample]/sum(nmf_matrix$contribution[,sample])
  #Pr(Mutation)

  #Bayes Formula Calculation
  prob <- a*b/c
  return(prob)
}
```

@@

```{r}
Bayes_function("G[C>T]G", "Signature A", "colon1", nmf_res, mut_mat)
Bayes_function("G[C>T]G", "Signature B", "colon1", nmf_res, mut_mat)
```
